We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-02-19 paper/paper.tex
references

The spatial distribution of satellite galaxies around our Milky Way
(MW) and the M31 galaxy provides a stringent test for structure
formation theories in a explicit cosmological context
\citep{2015ApJ...815...19P, 2016MNRAS.457.1931S}.
The presence of a Vast Polar Structure of satellites around the Milky
Way, first suggested by \cite{1976RGOB..182..241K} and
\cite{1976MNRAS.174..695L} as a Magellanic Plane, has been
stablished in the last decade \citep{2005A&A...431..517K,2013MNRAS.435.1928P}. 
This structure is present in the $11$ brightest "classical" dwarf
galaxies and has been confirmed as fainter satellites have been
detected \citep{2014MNRAS.441.2124B}. 
In the case of M31, observational studies have found a planar satellite
distribution in a subset of $15$ satellites out of the 
total poulation of $27$ satellites.\citep{2013ApJ...766..120C,
2013Natur.493...62I}, although its $11$ brightest satellites (to make
a fair comparison against the MW) do not show any special feature.

@@

>>>>

The spatial distribution of satellite galaxies around our Milky Way
(MW) and the M31 galaxy provides a stringent test for structure
formation theories in a explicit cosmological context
\citep{2015ApJ...815...19P, 2016MNRAS.457.1931S}.
The presence of a Vast Polar Structure of satellites around the Milky
Way, first suggested by \cite{1976RGOB..182..241K} and
\cite{1976MNRAS.174..695L} as a Magellanic Plane, has been
stablished in the last decade \citep{2005A&A...431..517K,2013MNRAS.435.1928P}. 
This structure is present in the $11$ brightest "classical" dwarf
galaxies and has been confirmed as fainter satellites have been
detected \citep{2014MNRAS.441.2124B}. 
In the case of M31, observational studies have found a planar satellite
distribution in a subset of $15$ satellites out of the 
total poulation of $27$ satellites.\citep{2013ApJ...766..120C,
2013Natur.493...62I}, although its brightest satellites
do not show any special feature and are consistent with a random
distribution \citep{2006AJ....131.1405K, 2007MNRAS.374.1125M}.

@@

\begin{table*}
\centering
\begin{tabular}{|p{3.0cm}|p{6cm}| p{4.5cm}| c|}\hline
Reference & Target Measurement & Parent Sample & Probability ($\%$)\\\hline
\text{\cite{2005A&A...431..517K}} & RMS height in MW's 11 classical
satellites & Monte Carlo from an spherical power law
radial distribution. & $<0.5$ \\
\text{\cite{2005MNRAS.363..146L}} & Triaxiality of MW's 11 classical
satellites & 6 high resolution DM only N-body simulations. & common \\
\text{\cite{2005ApJ...629..219Z}} & Triaxiality and disk height in
MW's 11 classical satellites & 3 high resolution DM only N-body
simulations. & 2 \\
\text{\cite{2006AJ....131.1405K}} & RMS height in M31's 15 brightest
satellites & Monte Carlo satellite distributions with a power law
radial distribution & $87-99$\\
\text{\cite{2007MNRAS.374.1125M}} & Triaxiality and RMS height in MW's
11-13 brightest satellites & Monte Carlo from a halo triaxiality distribution from LCDM
simulations & $<0.5$\\
\text{\cite{2007MNRAS.374.1125M}} & Triaxiality and RMS height in M31's
16 brightest satellites & Monte Carlo from an spherical power law radial
distribution & $17$\\
\hline
\end{tabular}
\caption{Probability results derived in previous publications.}
\end{table*}
